A Comparison of Different GANs for Generating Handwritten Digits on MNIST

### 2020-04-18 paper.tex
Added results of reducing dataset size by 1/6

@@

In this experiment we compare how the GAN algorithms run at different levels of training data from the MNIST set. We compare the GANS using the full training set, half the training set, and an eighth of the dataset. Each algorithm was given 25 epochs to run.

TODO: run experement

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.3\textwidth]{results/0.png}
    \caption{Output with no training data}%
    \label{fig:noData}%
\end{figure}

@@

In this experiment we compare how the GAN algorithms run at different levels of training data from the MNIST set. We compare the GANS using the full training set, and one sixth of the training data.

The full dataset contained roughly sixty thousand images and took 187200 batches of 64 images to run 200 epochs. The reduced dataset contained ten thousand images and took 31200 batches of 64 images to run 200 epochs.

Figures \ref{fig:ganResults} through \ref{fig:dcganResults} show the results of using all the data in the MNIST dataset on 200 epochs. Figure \ref{fig:reducedData} shows the result of the three algorithms at 200 epochs on the data set reduced to one sixth the original size. Despite reducing the amount of training data, the DCGAN still performed incredibly well, however the two other algorithms took a major performance hit.

\begin{figure*}[h!]
    \centering
     \subfloat[GAN]{{\includegraphics[width=0.3\textwidth]{results/reduced/gan.png}}}
    \qquad
   \subfloat[WGAN]{{\includegraphics[width=0.3\textwidth]{results/reduced/wgan.png}}}
    \qquad
    \subfloat[DCGAN]{{\includegraphics[width=0.3\textwidth]{results/reduced/dcgan.png}}}
    \caption{Results with one Sixth of Training Set and trained for 200 Epochs}%
    \label{fig:reducedData}%
\end{figure*}
